|

### 2025-01-24 doc/paper.qmd
paper enhance 1-3

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**DV**: Dependent Variable  
**HU**: Humboldt-Universität zu Berlin  
**IV**: Independent Variable  
**EU**: European Union  ##  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom  ##  
**WRDS**: Wharton Research Data Services

@@

The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment. @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper. The concluding remarks are provided in @sec-conclusion.

@@

This paper replicates Figure 3 from the European Commission’s [-@EC_Report_2024] report, which visualizes the market shares of audit firms — Big 4, CR4, and 10KAP — by the number of PIE statutory audits conducted in 2021 across EU countries and at the EU level. The replication provides insights into market concentration and the dominance of major audit firms, reflecting variations in audit practices and competition across Europe.

@@

# Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}
## Research Design Choices and Assumptions {#sec-research_design_assumptions2}
## Replication Steps {#sec-replication_steps2}
## Results {#sec-results2}

# Task 3 - Cross-Country Replication {#sec-task3}
## Research Design Choices and Assumptions {#sec-research_design_assumptions3}
## Replication Steps {#sec-replication_steps3}
## Results {#sec-results3}

>>>>

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**DV**: Dependent Variable  
**HU**: Humboldt-Universität zu Berlin  
**IV**: Independent Variable  
**EU**: European Union  ##  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom  ## 
**US**:: United States 
**WRDS**: Wharton Research Data Services

@@

The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment. @sec-task1 establishes baseline results by replicating key tables and figures from the original study using US data (1972–2006). @sec-task2 extends the analysis by applying the same methodology to 2007–2023 US data, enabling a comparison of how results evolve over time. @sec-task3 broadens the scope by applying the approach to a non-US country, requiring adjustments for different databases and market structures. Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper. The concluding remarks are provided in @sec-conclusion.

@@

Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using US data (1972–2006) to establish baseline results. This ensures alignment with the original findings before extending the analysis in later tasks. By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period.

@@

# Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}

This Section extends the analysis to 2007–2023, a period defined by major economic events such as the 2008 financial crisis and the COVID-19 pandemic, which may have influenced the informativeness of earnings announcements. While the task is relatively straightforward in terms of programming—requiring adjustments to the sample period—it demands careful economic interpretation of observed trends, market shifts, and potential structural changes that may influence the relationship between earnings announcements and stock returns.

## Research Design Choices and Assumptions {#sec-research_design_assumptions2}
## Replication Steps {#sec-replication_steps2}
## Results {#sec-results2}

# Task 3 - Cross-Country Replication {#sec-task3}

Task 3 extends the analysis beyond the United States by replicating Figure 1 using data from a non-U.S. market, providing insights into how earnings informativeness varies across different regulatory environments and market structures. This task requires mapping variables from CRSP/Compustat to their equivalents in Worldscope/Datastream, adjusting for differences in accounting standards, market liquidity, and institutional factors. While the core replication methodology remains the same, careful data handling and economic interpretation are crucial to account for cross-country differences.

## Research Design Choices and Assumptions {#sec-research_design_assumptions3}
## Replication Steps {#sec-replication_steps3}
## Results {#sec-results3}
